Live Functional Programming with Typed Holes

### 2018-04-30 discussion.tex
added acknowledgment of LIVE and OBT referees

The authors would like to thank the participants of the PL reading group at UChicago, Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton and Claire LeGoues for their insights and feedback on various iterations of this work.

>>>>

The authors would like to thank Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton and Claire LeGoues, the participants of the PL reading group at UChicago, and referees for talk proposals at the LIVE 2017 and Off the Beaten Track (OBT) 2017 workshops for their insights and feedback on various iterations of this work.
